The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-10-05 article.tex
Moved to methods, embedded in text

\item For each tree 
generated under the MBD model we aim to generate a "twin" tree under the BD model in order to perform the same analysis and compare the results. To do so we need to be sure that the comparison is fair. The method we adopt to achieve this goal is to impose that the amount of information used in the Bayesian information will be the same. These are the same number of taxa and the same (expected) 
number of DNA mutations. See appendix for the exact procedure.

\section{Creating twin trees}

To obtain twin trees with an equal amount of information, we impose
that the expected number of mutations in an MBD tree, $m_{MBD}$ equals
the expected number of mutations in a BD tree, $m_{BD}$:

>>>>

\item For each tree 
generated under the MBD model we aim to generate a "twin" tree under the BD model in order to perform a fair comparison, using trees 
with the same amount of information, 
which is the number of taxa 
and the same (expected) number of DNA mutations.
To obtain these twin trees, 
\richel{
  I suggest to first start with the equal number of taxa,
  and the calculation of the speciation rates first.
}
we impose
that the expected number of mutations in an MBD tree, $m_{MBD}$ equals
the expected number of mutations in a BD tree, $m_{BD}$:
